\section{System Model}
We consider a time-slotted UAV-swarm service system. Time slots are indexed by $t=1,2,\ldots,T$. A high-altitude platform or edge controller observes the state of heterogeneous UAV swarms, moving users, content requests, cache states, and weather. It then assigns UAV swarms to active demand clusters.

Let $\mathcal{S}=\{1,\ldots,S\}$ denote the set of UAV swarms. Each swarm $s\in\mathcal{S}$ has a position $\vect{p}_{s,t}$, bandwidth $W_s$, transmit power $P_s$, residual energy $E_{s,t}$, cache $\mathcal{C}_{s,t}$, service capacity, current load $L_{s,t}$, and previous assignments. The altitude is limited to $[h_{\min},h_{\max}]$. Users and vehicles move according to a Gauss--Markov mobility model, which is commonly used to represent correlated movement in mobile ad hoc simulations \cite{camp2002mobility}.

At slot $t$, active requesting users are grouped into demand clusters $\mathcal{K}_t$. Cluster $k\in\mathcal{K}_t$ has centroid $\vect{u}_{k,t}$, demand arrival $A_{k,t}$, deadline $\tau_{k,t}$, priority, requested files, and backlog $Q_{k,t}$. The binary variable $x_{s,k,t}\in\{0,1\}$ is one if swarm $s$ serves cluster $k$ at slot $t$. Each cluster is assigned to at most one swarm:
\begin{equation}
\sum_{s\in\mathcal{S}} x_{s,k,t} \leq 1, \quad \forall k\in\mathcal{K}_t.
\label{eq:assignment_one}
\end{equation}

The backlog evolves as
\begin{equation}
Q_{k,t+1}=\left[Q_{k,t}+A_{k,t}-\mu_{k,t}\right]^+,
\label{eq:queue_update}
\end{equation}
where $\mu_{k,t}=\sum_s x_{s,k,t}\mu_{s,k,t}$ is the served traffic and $[y]^+=\max(y,0)$. Traffic that remains after the deadline is counted as dropped.

The air-to-ground channel uses distance-based path loss, line-of-sight probability, weather attenuation, speed mismatch penalty, and random shadowing. Let $m_{s,k,t}$ be the observed link margin between swarm $s$ and cluster $k$. The service estimate is
\begin{equation}
\mu_{s,k,t}=R_{s,k,t}\left(1-\hat{p}^{\mathrm{out}}_{s,k,t}\right),
\label{eq:service_rate}
\end{equation}
where $R_{s,k,t}$ is the link capacity and $\hat{p}^{\mathrm{out}}_{s,k,t}$ is the predicted outage probability.

The cache value for a swarm-cluster pair is
\begin{align}
V^{\mathrm{cache}}_{s,k,t}={}&\left(1-\hat{p}^{\mathrm{out}}_{s,k,t}\right)
\Big(a_1H^{\mathrm{local}}_{s,k,t}+a_2H^{\mathrm{nbr}}_{s,k,t} \nonumber\\
&-a_3S_{s,k,t}-a_4N_{s,k,t}\Big),
\label{eq:cache_value}
\end{align}
where $H^{\mathrm{local}}$ is the valid local service hit ratio, $H^{\mathrm{nbr}}$ is the neighbor-cache reuse ratio, $S$ is a stale-cache penalty, and $N$ is a neighbor-fetch penalty. This form makes cache useful only when it can reduce delay or energy under the predicted link condition.

The switch cost is
\begin{equation}
C^{\mathrm{sw}}_{s,k,t}=\mathbb{1}\{s\neq s^{\mathrm{prev}}_{k,t}\}\left(c_0+c_1d_{s,k,t}+c_2\right),
\label{eq:switch_cost}
\end{equation}
where $s^{\mathrm{prev}}_{k,t}$ is the previous serving swarm of the persistent cluster and $d_{s,k,t}$ is the distance. No handover is counted for a newly born cluster. Energy and delay are represented as additive costs:
\begin{align}
C^{\mathrm{en}}_{s,k,t} &= C^{\mathrm{tx}}_{s,k,t}+C^{\mathrm{move}}_{s,k,t}+C^{\mathrm{fetch}}_{s,k,t},\label{eq:energy_cost}\\
D_{s,k,t} &= D^{\mathrm{deadline}}_{k,t}+D^{\mathrm{queue}}_{s,t}+D^{\mathrm{miss}}_{s,k,t}+\hat{p}^{\mathrm{out}}_{s,k,t}.\label{eq:delay_cost}
\end{align}
Table~\ref{tab:notation} lists the main symbols.

\input{tables/notation_table}
